---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# cheer

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

The `praise.me` package is created for teaching demo purposes. It extends the idea of the `praise` package but includes: 

- the use of `cowsay` package to demonstrate the use of imported package,
- the use of special `print` method,
- the use of tags `@descripton`, `@param`, `@return`, `@rdname` from `roxygen2`,
- the concept of turning repeated steps into an internal function (e.g. `praise_now()`),
- distribution and documentation of data,
- simple tests via `testthat`, 
- a vignette, and
- a `pkgdown` website.

## Installation

You can install the development version of cheer like so:

``` r
remotes::install_github("emitanaka/praise.me")
```

## Example

Give yourself or others a simple praise:

```{r example, message = FALSE}
library(praise.me)
praise_me()
praise_me(by = "chicken")
praise_someone(who = "Natalia", by = "cow")
```
