---
title: "Start your RStudio Session with a Positive Affirmation"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Positive affirmation}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Why positive affirmation

Positive affirmation are positive phrases that are typically repeated to affirm something to be true. Scientific research has some empirical evidence that positive affirmation can:

1. Decreate health-deteriorating stress [(Salleh 2008)](https://www.ncbi.nlm.nih.gov/pmc/articles/PMC3341916/)
2. Control self-sabotaging thoughts and speech
3. Reduce anxiety
4. Improve mood [(Cohen & Sherman 2014)](https://depts.washington.edu/anesth/edi/_resources-docs/Cohen_annurev-psych-010213-115137.pdf)
5. Promote positive coping
6. Enhance self-esteem [(Cascio et al. 2016)](https://www.ncbi.nlm.nih.gov/pmc/articles/PMC4814782/)
7. Improve problem-solving under stress
8. Can help you find love
9. May change outcomes


This vignette is based on this [blog post by Sarah Kristenson](https://www.happierhuman.com/benefits-affirmations/).


## Get a positive affirmation for every RStudio session start

The `cheer` package includes functions to give you or someone else a praise. You can append your session start up message to include a positive affirmation every time by modifying your R profile. To do this, first use the following command to locate and open your R profile.

```{r, eval = FALSE}
usethis::edit_r_profile()
```

Then in your `.Rprofile` file, add the following code.

```{r, eval = FALSE}
setHook("rstudio.sessionInit", function(newSession) {
  # any code included here will be run at the start of each RStudio session
  cat(cli::col_green(cheer::praise_me()))
}, action = "append")
```

Now try restarting your RStudio session. You should now see a positive affirmation colored green! Feel free to change to what you like. 

If you want more ideas of what to include in your RStudio session start up then check out this blog post [here](https://damien-datasci-blog.netlify.app/post/2020-12-31-pimp-your-r-startup-message/).
